`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-12-16 inst/manuscript/manuscript.rmd
Minor reformatting;

# Figure legends
```{r figure1-creation, echo=FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
# Plot spectral traces (Figure 1)
figure1_plot <- scramblase_assay_traces(
  template_file,
  time_max_sec = 350)
grid::rectGrob(
    width = grid::unit(0.1, "mm"),
    height = grid::unit(0.1, "mm")) %>%
  grid::grid.draw()
```
```{r figure1-save, echo=FALSE}
ggsave(
  plot = figure1_plot,
  filename = file.path("figures", "Cotton_et_al_-_flippant_-_Figure1.png"),
  width = 177.2,
  units = "mm",
  dpi = 600)
```

```{r figure2-creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details). In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
figure2_plot %<>% multipanelfigure::add_panel(
  top_panel = 1,
  panel = flippant::scramblase_assay_plot(template_file) + 
    ggplot2::theme_bw() + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])))
figure2_plot %<>% multipanelfigure::add_panel(
  top_panel = 2,
  panel = flippant::scramblase_assay_plot(template_file, split_by_experiment = FALSE) + 
    ggplot2::theme_bw() + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])) +
    ggplot2::facet_wrap(c("`Experimental Series`"))+
    ggplot2::guides(colour = "none"))
grid::rectGrob(
    width = grid::unit(0.1, "mm"),
    height = grid::unit(0.1, "mm")) %>%
  grid::grid.draw()
```
```{r figure2-save, echo=FALSE}
ggsave(
  plot = figure2_plot,
  filename = file.path("figures", "Cotton_et_al_-_flippant_-_Figure2.png"),
  width = figure2_plot %>%
    multipanelfigure::simple_grob_width(),
  height = figure2_plot %>%
    multipanelfigure::simple_grob_height(),
  units = "mm",
  dpi = 600)
```

>>>>

# Figure legends
```{r figure1-creation, echo=FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
# Plot spectral traces (Figure 1)
figure1_plot <- scramblase_assay_traces(
  template_file,
  time_max_sec = 350)
grid::rectGrob(
    width = grid::unit(0.1, "mm"),
    height = grid::unit(0.1, "mm")) %>%
  grid::grid.draw()
```

```{r figure1-save, echo=FALSE}
ggsave(
  plot = figure1_plot,
  filename = file.path("figures", "Cotton_et_al_-_flippant_-_Figure1.png"),
  width = 177.2,
  units = "mm",
  dpi = 600)
```

```{r figure2-creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details). In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
figure2_plot %<>% multipanelfigure::add_panel(
  top_panel = 1,
  panel = flippant::scramblase_assay_plot(template_file) + 
    ggplot2::theme_bw() + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])))
figure2_plot %<>% multipanelfigure::add_panel(
  top_panel = 2,
  panel = flippant::scramblase_assay_plot(template_file, split_by_experiment = FALSE) + 
    ggplot2::theme_bw() + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])) +
    ggplot2::facet_wrap(c("`Experimental Series`"))+
    ggplot2::guides(colour = "none"))
grid::rectGrob(
    width = grid::unit(0.1, "mm"),
    height = grid::unit(0.1, "mm")) %>%
  grid::grid.draw()
```

```{r figure2-save, echo=FALSE}
ggsave(
  plot = figure2_plot,
  filename = file.path("figures", "Cotton_et_al_-_flippant_-_Figure2.png"),
  width = figure2_plot %>%
    multipanelfigure::simple_grob_width(),
  height = figure2_plot %>%
    multipanelfigure::simple_grob_height(),
  units = "mm",
  dpi = 600)
```
